Language-Based Security for Low-Level MPC

### 2024-05-14 ppdp24/example-bdoz.tex
checkpoint

With these conventions, our BDOZ library is defined in Figure \ref{fig-bdoz}.

@@

\begin{definition}[BDOZ preprocessing]
  Define:
  \begin{mathpar}
    \mathit{shares} \defeq
    \{ \elab{\mesg{w}}{\cid}\ |\ \cid \in \{ 1, 2 \} \wedge w \in \{ a,b,c,x,y \}  \}

>>>>

With these conventions, our BDOZ library is defined in Figure \ref{fig-bdoz}.
In $\metaprot$ we represent BDOZ share, MAC pairs as records:
$$
\ttt{\{ share = }v\ttt{;  mac =}\ m \ttt{\}}
$$
and we define $\ttt{macsum}$ for addition of shares,
$\ttt{maccsum}$ for addition of a share and a constant, and
$\ttt{macctimes}$ for multiplication of a share and a constant
in the BDOZ encryption scheme \cite{XXX}. The $\ttt{auth}$
function implements the MAC check as an $\assert$.

We also define a function $\ttt{secopen}$ to implement ``secure
opening''.  In this standard subprotocol, the value
$\macgv{\secret{w_1}} \fplus \macgv{\mesg{w_2}}$ is reconstructed as
$\mesg{w_3}$, by each client $\cid_2$ communicating
$\lcod{\mesg{w_1} + \mesg{w_2}}{\cid_2}$ to $\cid_1$.  Assuming that
$\macgv{\mesg{w_2}}$ is in an independent uniform distribution,
this perfectly hides $\secret{w_1}$. In a mutiplication gate
either $a$ or $b$ of a Beaver triple are used in secure opening,
so, e.g., given $
(\varnothing,\ttt{secopen}(a, x, d, 2, 1) \redxs (\prog,())$
we have both:
\begin{mathpar}
  \conddetx{\progtt(\prog)}{\{\macgv{\mesg{a}},\elab{\secret{x}}{1} \}}{\{ \elab{\mesg{d}}{2} \}}

  \sep{\progtt(\prog)}{\{ \elab{\mesg{d}}{2} \}}{\{ \elab{\secret{x}}{1}  \}}
\end{mathpar}
Furthermore, client 2's authentication of the sum of shares with the
sum of their keys detects any attempted cheating by $1$.
Finally, the $\ttt{secreveal}$ function
is very similar to $\decodegmw$, except with the addition
of authentication of revealed shares to ensure malicious security.

@@

The full protocol for malicious secure product of secrets $x$ (that
is, $\elab{\secret{x}}{1}$) and $y$ (that is, $\elab{\secret{y}}{2}$)
using Beaver triple $a,b,c$ is defined in Figure \ref{fig-bdoz}. Both
parties interact in secure opening of $x \fplus a$ and $y + b$,
followed by local computation to compute their share of the $x * y$
using only local addition and product as per standard protocol
\cite{XXX}. The non-interactive reconstruction of the local authentication
key for both the secure openings and the final reveal is enabled by the
semi-homorphic properties of the BDOZ scheme.

\subsection{Cheating Detection and Integrity}
